Effects of Different Pain Relievers and Dosages on Cognitive Retention

### 2025-03-11 paper/paper.qmd
minor changes

# Step 4: Display the table
kable(improvement_summary, booktabs = TRUE, row.names = FALSE)

@@

ggplot(clean_data, aes(x = Drug, y = CardScore, fill = Time)) +
  geom_boxplot(position = position_dodge(width = 0.8)) +
  labs(
    title = "Memory Card Scores Before and After Treatment by Drug Type",
    x = "Drug Type",
    y = "Memory Card Score",
    fill = "Time"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 12)
  )

>>>>

kable(improvement_summary, booktabs = TRUE, row.names = FALSE)

@@

ggplot(clean_data, aes(x = Drug, y = CardScore, fill = Time)) +
  geom_boxplot(position = position_dodge(width = 0.8)) +
  labs(
    title = "Memory Card Scores Before and After Treatment by Drug Type",
    x = "Drug Type",
    y = "Memory Card Score",
    fill = "Time"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 12)
  )
```
